---
title: "Case Study Analysis"
author: "Arfa Aijazi"
date: "November 2022"
output:
  html_document:
    df_print: paged
---
This script completes all data analysis related to the two case studies as described in the paper.

### Setup
Load libraries
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
library(knitr)
library(zoo)
library(forcats)
library(gridExtra)
library(Metrics)
library(comf)
library(ggpubr)
```

Set plot theme and colors
```{r echo=TRUE, message=FALSE, warning=FALSE}
theme_custom = function() {
  theme_minimal() %+replace%
    theme(legend.position = "top") +
    theme(panel.grid = element_blank()) +
    theme(strip.background = element_blank()) +
    theme(panel.border = element_blank()) +
    theme(panel.background = element_blank()) +
    theme(legend.title = element_blank()) +
    theme(text = element_text(size = 7, colour = "#000000")) +
    theme(plot.margin = margin(t = 0, r = 0.1, b = 0, l = 0.1))
}
```

### Dallas 2021 Case Study
Load EnergyPlus model outputs
```{r echo=TRUE, message=FALSE, warning=FALSE}

dalls_epoutput_file <- "../data/case_study/dallas_energymodel/Dallas_Feb2021_Outage_KDFW/Dallas_Feb2021_Outage_KDFW.csv"
dallas_epoutput <- read_csv(file = dalls_epoutput_file) 

colnames(dallas_epoutput) <- c("Date.Time", "DBT", "T.Air", "T.Attic", "Electricity.Facility", "Electricity.Building", "Electricity.Zone", "Electricity.General", "Electricity.HVAC", "Electricity.Plant")

dallas <- dallas_epoutput %>%
  mutate(Date = str_extract(Date.Time, "^[^\\s]+")) %>%
  mutate(Time = str_extract(Date.Time, "\\s.+")) %>%
  mutate(Date = paste0(Date,"/2021")) %>%
  mutate(Date.Time = paste(Date, Time, sep = " ")) %>%
  mutate(Date.Time = parse_date_time(Date.Time, "mdy_HMS")) %>%
  select(Date.Time, DBT, T.Air, Electricity.Facility) %>%
  filter(between(Date.Time, parse_date_time("2021-02-11", "ymd"), parse_date_time("2021-02-23", "ymd"))) %>%
  mutate(T.skin_Baseline = 32.74228) %>%
  mutate(h.body_Baseline = 3.645669) %>%
  mutate(Q_Baseline = h.body_Baseline*(T.skin_Baseline - T.Air)) %>%
  mutate(h.cal_Baseline = 7.976792) %>%
  mutate(T.eq_Baseline = T.skin_Baseline - (Q_Baseline/h.cal_Baseline)) %>%
  mutate(T.skin_Passive = 34.60110) %>%
  mutate(h.body_Passive = 1.341360) %>%
  mutate(Q_Passive = h.body_Passive*(T.skin_Passive - T.Air)) %>%
  mutate(h.cal_Passive = 7.621755) %>%
  mutate(T.eq_Passive = T.skin_Passive - (Q_Passive/h.cal_Passive)) %>%
  mutate(thermal.effect_Passive = T.eq_Passive - T.eq_Baseline) %>%
  mutate(thermal.effect_Passive = ifelse(Electricity.Facility == 0, thermal.effect_Passive, 0)) %>%
  mutate(thermal.effect_Passive = ifelse(hour(Date.Time) >= 22 | hour(Date.Time) < 7, thermal.effect_Passive, 0)) %>%
  mutate(T.Air_Passive = T.Air + thermal.effect_Passive) %>%
  mutate(T.skin_HeatedBlanket = 34.05160) %>%
  mutate(h.body_HeatedBlanket = 1.992226) %>%
  mutate(Q_HeatedBlanket = h.body_HeatedBlanket*(T.skin_HeatedBlanket - T.Air)) %>%
  mutate(h.cal_HeatedBlanket = 7.976792) %>%
  mutate(T.eq_HeatedBlanket = T.skin_HeatedBlanket - (Q_HeatedBlanket/h.cal_HeatedBlanket)) %>%
  mutate(thermal.effect_HeatedBlanket = T.eq_HeatedBlanket - T.eq_Baseline) %>%
  mutate(thermal.effect_HeatedBlanket = ifelse(Electricity.Facility == 0, thermal.effect_HeatedBlanket, 0)) %>%
  mutate(thermal.effect_HeatedBlanket = ifelse(hour(Date.Time) >= 22 | hour(Date.Time) < 7, thermal.effect_HeatedBlanket, 0)) %>%
  mutate(T.Air_HeatedBlanket = T.Air + thermal.effect_HeatedBlanket) %>%
  mutate(T.skin_HeatedBlanketPassive = 34.84524) %>%
  mutate(h.body_HeatedBlanketPassive = 1.120498) %>%
  mutate(Q_HeatedBlanketPassive = h.body_HeatedBlanketPassive*(T.skin_HeatedBlanketPassive - T.Air)) %>%
  mutate(h.cal_HeatedBlanketPassive = 7.621755) %>%
  mutate(T.eq_HeatedBlanketPassive = T.skin_HeatedBlanketPassive - (Q_HeatedBlanketPassive/h.cal_HeatedBlanketPassive)) %>%
  mutate(thermal.effect_HeatedBlanketPassive = T.eq_HeatedBlanketPassive - T.eq_Baseline) %>%
  mutate(thermal.effect_HeatedBlanketPassive = ifelse(Electricity.Facility == 0, thermal.effect_HeatedBlanketPassive, 0)) %>%
  mutate(thermal.effect_HeatedBlanketPassive = ifelse(hour(Date.Time) >= 22 | hour(Date.Time) < 7, thermal.effect_HeatedBlanketPassive, 0)) %>%
  mutate(T.Air_HeatedBlanketPassive = T.Air + thermal.effect_HeatedBlanketPassive)
```
Calculate degree-hours of exposure to temperatures below WHO minimum indoor temperature recommendation of 18C during sleeping hours (10pm - 7am)
```{r echo=TRUE, message=FALSE, warning=FALSE}
dallas_exposure <- dallas %>%
  select(Date.Time, starts_with("T.Air")) %>%
  filter(hour(Date.Time) >= 22 | hour(Date.Time) < 7) %>%
  rename(T.Air_None = T.Air) %>%
  pivot_longer(!Date.Time, names_to = "Type", values_to = "Temperature") %>%
  mutate(exposure = 18 - Temperature) %>%
  mutate(exposure = ifelse(exposure > 0, exposure, 0)) %>%
  group_by(Type) %>%
  mutate(Type = factor(Type, levels = rev(c("DBT", "T.Air_None", "T.Air_Passive", "T.Air_HeatedBlanket", "T.Air_HeatedBlanketPassive")))) %>%
  summarise(exposure = sum(exposure))
```

Calculate percent change in cold exposure relative to baseline
```{r echo=TRUE, message=FALSE, warning=FALSE}
dallas_exposure <- dallas_exposure %>%
  arrange(desc(exposure)) %>%
  mutate(percent.reduction = 100*(exposure-dallas_exposure$exposure[1])/dallas_exposure$exposure[1])
```

Prepare data for plot and plot cold exposure by intervention type
```{r echo=TRUE, message=FALSE, warning=FALSE}
dallas_exposure$Type2 = c("None", "Active", "Passive", "Passive + Active")
dallas_exposure$Type2 = factor(dallas_exposure$Type2, levels = c("None", "Passive", "Active", "Passive + Active"))

dallas_exposure$Label = c("None", "Heated blanket (on)", "Passive combination", "Passive combination + Heated blanket")

dallas_exposure <- dallas_exposure %>%
  mutate(Label = fct_reorder(Label, exposure))

dallas_exposure$percent.reduction[1] = NA

dallas_exposure_plot <- ggplot(dallas_exposure, aes(x = Label, y = exposure)) + 
  geom_col(aes(fill = Type2), width = 0.5) +
  geom_text(aes(label = round(percent.reduction)), hjust = -0.5) +
  scale_fill_manual(values = c("#bbbbbb", "#ee833d", "#59abb7", "#495893")) +
  scale_y_continuous(breaks = seq(0, 600, 300), limits = c(0, 650)) +
  scale_x_discrete(labels = function(Label) str_wrap(Label, width = 20)) +
  theme_custom() +
  ylab("Sleep time heat/cold exposure (degree-hours)") +
  theme(axis.title = element_blank()) +
  theme(legend.position = "none") +
  coord_flip() 
```

Prepare data for plot and plot temperature and effective temperature over time
```{r echo=TRUE, message=FALSE, warning=FALSE}
dallas_plot <- dallas %>%
  select(Date.Time, DBT, T.Air, T.Air_Passive) %>%
  rename(T.Air_None = T.Air) %>%
  mutate(WHO = 18) %>%
  pivot_longer(!Date.Time, names_to = "Type", values_to = "Temperature") %>%
  mutate(Type = factor(Type, levels = c("DBT", "WHO", "T.Air_None", "T.Air_Passive")))

dallas_timeseries_plot <- ggplot(dallas_plot, aes(x = Date.Time, y = Temperature)) +
  annotate("rect", xmin = parse_date_time("2021-02-14 1:00", "ymd_HM"), xmax = parse_date_time("2021-02-20 0:00", "ymd_HM"), ymin = -Inf, ymax = Inf, alpha = 0.2, fill = "#d1e5f0") +
  annotate("text", x = parse_date_time("2021-02-14 12:00", "ymd_HM"), y = Inf, label = "Power outage") +
  geom_line(aes(linetype = Type, colour = Type)) + 
  scale_colour_manual(values = c("#d9f0d3", "#e7d4e8", "#000000", "#ee833d")) +
  xlim(c(parse_date_time("2021-02-11", "ymd"), parse_date_time("2021-02-23", "ymd"))) +
  scale_y_continuous(breaks = seq(-20, 25, 5), limits = c(-20, 25)) +
  theme_custom() +
  theme(axis.title = element_blank()) +
  theme(panel.grid.major.y = element_line(colour = "#f7f7f7"))

```

### Karachi 2015 Case Study
Load ASHRAE thermal comfort database v2 data
```{r echo=TRUE, message=FALSE, warning=FALSE}
# Read in metadata from Github as data table
df_meta <- read_csv("https://github.com/CenterForTheBuiltEnvironment/ashrae-db-II/raw/master/v2.1.0/db_metadata.csv")

# Read in database from Github as data table
df_measurements <- read_csv("https://github.com/CenterForTheBuiltEnvironment/ashrae-db-II/raw/master/v2.1.0/db_measurements_v2.1.0.csv.gz")
```

Clean-up and subset downloaded data
```{r echo=TRUE, message=FALSE, warning=FALSE}
# Subset records with indoor air temperature and meteorological data
df_acm2 <- df_measurements %>%
  filter(!is.na(ta) & 
           (!is.na(t_out_isd)|!is.na(t_out)))

# Collapse outdoor met data
df_acm2 <- df_acm2 %>%
  mutate(t_out_combined = case_when(!is.na(t_out_isd) ~ t_out_isd,
                                    is.na(t_out_isd) & !is.na(t_out) ~ t_out,
                                    TRUE ~ NA_real_)) %>%
  select(-c(t_out_isd, t_out))

# Add relevant parameters from metadata table
df_acm2 <- df_meta %>%
  select(building_id, region, country, city, building_type, cooling_type, records, climate) %>%
  left_join(df_acm2, ., by = "building_id")

# Subset records from multifamily buildings in hot arid or semi-arid climate
df_karachi <- df_acm2 %>%
  filter(building_type == "multifamily housing") %>%
  filter(climate == "hot semi-arid" | climate == "desert (hot arid)") %>%
  filter(cooling_type == "naturally ventilated") %>%
  select(building_id, building_type, cooling_type, region, country, city, climate, timestamp, season, ta, tr, rh, t_out_combined)
```

Linear model of indoor air temperature wrt outdoor temperature
```{r echo=TRUE, message=FALSE, warning=FALSE}
lm_karachi_ta <- lm(ta ~ t_out_combined, data = df_karachi, na.action = na.exclude)
summary(lm_karachi_ta)

a_ta <- lm_karachi_ta$coefficients[2]
b_ta <- lm_karachi_ta$coefficients[1]
r2_ta <- summary(lm_karachi_ta)$r.squared
MAE_ta <- mae(df_karachi$ta, predict(lm_karachi_ta, newdata = df_karachi))
```

Linear model of indoor radiant temperature wrt outdoor temperature
```{r echo=TRUE, message=FALSE, warning=FALSE}
lm_karachi_tr <- lm(tr ~ t_out_combined, data = df_karachi, na.action = na.exclude)
summary(lm_karachi_tr)

a_tr <- lm_karachi_tr$coefficients[2]
b_tr <- lm_karachi_tr$coefficients[1]
r2_tr <- summary(lm_karachi_tr)$r.squared
MAE_tr <- mae(df_karachi$tr, predict(lm_karachi_tr, newdata = df_karachi))
```

Plot indoor air temperature wrt outdoor temperature
```{r echo=TRUE, message=FALSE, warning=FALSE}
ggplot(df_karachi, aes(x = t_out_combined, y = ta)) + 
  xlim(9, 40) +
  ylim(9, 40) +
  xlab("Outdoor air temperature, To (C)") +
  ylab("Indoor air temperature, Ta (C)") +
  geom_point(colour = "#bbbbbb") +
  geom_smooth(method = "lm", se = FALSE, colour = "#DDAA33") +
  annotate("text", x = 10, y = 40, label = paste0("Ta = ", round(a_ta, 1)," x To + ", round(b_ta, 1)), colour = "#4d4d4d") +
  #annotate("text", x = 10, y = 38, label = paste0("MAE = ", round(MAE_ta, 1), "C"), colour = "#4d4d4d") +
  annotate("text", x = 10, y = 38, label = paste0("R2 = ", round(r2_ta, 2)), colour = "#4d4d4d") +
  annotate("text", x = 30, y = 10, label = paste0("Based on ", nrow(df_karachi), " observations of naturally ventilated multifamily housing in hot semi-arid climate"), colour = "#4d4d4d") +
  theme_custom()
```

Plot indoor radiant temperature wrt outdoor temperature 
```{r echo=TRUE, message=FALSE, warning=FALSE}
ggplot(df_karachi, aes(x = t_out_combined, y = tr)) + 
  xlim(9, 40) +
  ylim(9, 40) +
  xlab("Outdoor air temperature, To (C)") +
  ylab("Mean radiant temperature, Tr (C)") +
  geom_point(colour = "#bbbbbb") +
  geom_smooth(method = "lm", se = FALSE, colour = "#AA3377") +
  annotate("text", x = 10, y = 40, label = paste0("Tr = ", round(a_tr, 1)," x To + ", round(b_tr, 1)), colour = "#4d4d4d") +
  #annotate("text", x = 10, y = 38, label = paste0("MAE = ", round(MAE_tr, 1), "C"), colour = "#4d4d4d") +
  annotate("text", x = 10, y = 38, label = paste0("R2 = ", round(r2_tr, 2)), colour = "#4d4d4d") +
  annotate("text", x = 30, y = 10, label = paste0("Based on ", nrow(df_karachi), " observations of naturally ventilated multifamily housing in hot semi-arid climate"), colour = "#4d4d4d") +
  theme_custom()
```

Download historical weather data from June 2015 and model indoor air temperature using the above linear model
```{r echo=TRUE, message=FALSE, warning=FALSE}
historical_file <- "../data/case_study/Karachi_June2015_OPKC.csv"
karachi_June2015 <- read.csv(file = historical_file, header = TRUE) %>%
  filter(stations == "OPKC") %>%
  rename(DBT = temp) %>%
  rename(RH_DBT = humidity) %>%
  rename(Date.Time = datetime) %>%
  select(-stations) %>%
  mutate(Date.Time = str_replace(Date.Time, "T", " ")) %>%
  mutate(Date.Time = parse_date_time(Date.Time, "ymd_HMS")) %>%
  mutate(T.Air = (DBT * a_ta) + b_ta) %>%
  mutate(ps_DBT = 610.78*exp(DBT/(DBT + 238.3) * 17.2694)) %>%
  mutate(p = (RH_DBT/100) * ps_DBT) %>%
  mutate(ps_T.Air = 610.78*exp(T.Air/(T.Air + 238.3) * 17.2694)) %>%
  mutate(RH_T.Air = (p/ps_T.Air)*100) 
```

Calculate cooling effect based on modeled SET from the comf package. Inputs for the SET model come from the linear model for indoor air temperature and indoor radiant temperature above and experimental conditions.

Baseline
```{r echo=TRUE, message=FALSE, warning=FALSE}
baselineCond <- createCond()
baselineCond$ta <- karachi_June2015$T.Air
baselineCond$tr <- karachi_June2015$T.Air
baselineCond$vel <- 0.1
baselineCond$rh <- karachi_June2015$RH_T.Air
baselineCond$met <- 0.7
baselineCond$clo <- 1.2

baselineSET <- calcComfInd(baselineCond, request = "set") 
karachi_June2015$baseline <- baselineSET$set
```

Passive combination
```{r echo=TRUE, message=FALSE, warning=FALSE}
passiveCond <- createCond()
passiveCond$ta <- karachi_June2015$T.Air
passiveCond$tr <- karachi_June2015$T.Air
passiveCond$vel <- 0.1
passiveCond$rh <- karachi_June2015$RH_T.Air
passiveCond$met <- 0.7
passiveCond$clo <- 0.34

passiveSET <- calcComfInd(passiveCond, request = "set") 
karachi_June2015$passiveSET <- passiveSET$set
```

Ceiling fan
```{r echo=TRUE, message=FALSE, warning=FALSE}
ceilingFanCond <- createCond()
ceilingFanCond$ta <- karachi_June2015$T.Air
ceilingFanCond$tr <- karachi_June2015$T.Air
ceilingFanCond$vel <- 0.4
ceilingFanCond$rh <- karachi_June2015$RH_T.Air
ceilingFanCond$met <- 0.7
ceilingFanCond$clo <- 1.2

ceilingFanSET <- calcComfInd(ceilingFanCond, request = "set") 
karachi_June2015$ceilingFanSET <- ceilingFanSET$set
```

Ceiling fan + passive combination
```{r echo=TRUE, message=FALSE, warning=FALSE}
ceilingFanPassiveCond <- createCond()
ceilingFanPassiveCond$ta <- karachi_June2015$T.Air
ceilingFanPassiveCond$tr <- karachi_June2015$T.Air
ceilingFanPassiveCond$vel <- 0.4
ceilingFanPassiveCond$rh <- karachi_June2015$RH_T.Air
ceilingFanPassiveCond$met <- 0.7
ceilingFanPassiveCond$clo <- 0.34

ceilingFanPassiveSET <- calcComfInd(ceilingFanPassiveCond, request = "set") 
karachi_June2015$ceilingFanPassiveSET <- ceilingFanPassiveSET$set
```

Calculate cooling effect
```{r echo=TRUE, message=FALSE, warning=FALSE}
karachi_June2015 <- karachi_June2015 %>%
  filter(between(Date.Time, parse_date_time("2015-06-14", "ymd"), parse_date_time("2015-06-27", "ymd"))) %>%
  pivot_longer(ends_with("SET"), names_to = "Type", values_to = "SET") %>%
  mutate(CoolingEffect = baseline - SET) %>%
  mutate(CoolingEffect = ifelse(between(Date.Time, parse_date_time("2015-06-17", "ymd"), parse_date_time("2015-06-24", "ymd")), CoolingEffect, 0)) %>%
mutate(CoolingEffect = ifelse(hour(Date.Time) >= 22 | hour(Date.Time) < 7, CoolingEffect, 0))%>%
  mutate(Type = substring(Type, 1, nchar(Type)-3)) %>%
  mutate(T.Air2 = T.Air - CoolingEffect) %>%
  select(Date.Time, DBT, T.Air, Type, T.Air2) %>%
  pivot_wider(names_from = Type, values_from = T.Air2) %>%
  rename(T.Air_None = T.Air, T.Air_Passive = passive, T.Air_ceilingFan = ceilingFan, T.Air_ceilingFanPassive = ceilingFanPassive)
  
```

Calculate degree-hours of exposure to temperatures above WHO minimum indoor temperature recommendation of 30C during sleeping hours (10pm - 7am)
```{r echo=TRUE, message=FALSE, warning=FALSE}
karachi_exposure <- karachi_June2015 %>%
  filter(between(Date.Time, parse_date_time("2015-06-17", "ymd"), parse_date_time("2015-06-24", "ymd"))) %>%
  filter(hour(Date.Time) >= 22 | hour(Date.Time) < 7) %>%
  filter(DBT != 25) %>%
  select(Date.Time, starts_with("T.Air")) %>%
  pivot_longer(!Date.Time, names_to = "Type", values_to = "Temperature") %>%
  mutate(exposure = Temperature - 30) %>%
  mutate(exposure = ifelse(exposure > 0, exposure, 0)) %>%
  group_by(Type) %>%
  mutate(Type = factor(Type, levels = c("T.Air_None", "T.Air_Passive", "T.Air_ceilingFan", "T.Air_ceilingFanPassive"))) %>%
  summarise(exposure = sum(exposure)) %>%
  mutate(exposure = round(exposure, 0))
```

Calculate percent change in heat exposure relative to baseline and prepare data for plot
```{r echo=TRUE, message=FALSE, warning=FALSE}
karachi_exposure <- karachi_exposure %>%
  arrange(desc(exposure)) %>%
  mutate(percent.reduction = 100*(exposure - karachi_exposure$exposure[1])/karachi_exposure$exposure[1]) 
  
karachi_exposure$Type2 = c("None", "Active", "Passive", "Passive + Active")
karachi_exposure$Type2 = factor(karachi_exposure$Type2, levels = c("None", "Passive", "Active", "Passive + Active"))

karachi_exposure$Label = c("None", "Ceiling fan", "Passive combination", "Passive combination + Ceiling fan")

karachi_exposure <- karachi_exposure %>%
  mutate(Label = fct_reorder(Label, exposure))

karachi_exposure$percent.reduction[1] = NA
```

Plot heat exposure by intervention type
```{r echo=TRUE, message=FALSE, warning=FALSE}
karachi_exposure_plot <- ggplot(karachi_exposure, aes(x = Label, y = exposure)) + 
  geom_col(aes(fill = Type2), width = 0.5) +
  geom_text(aes(label = round(percent.reduction)), hjust = -0.5) +
  scale_fill_manual(values = c("#bbbbbb", "#ee833d", "#59abb7", "#495893")) +
  scale_y_continuous(breaks = seq(0, 600, 300), limits = c(0, 650)) +
  scale_x_discrete(labels = function(Label) str_wrap(Label, width = 20)) +
  theme_custom() +
  theme(axis.title = element_blank()) +
  theme(legend.position = "none") +
  coord_flip() 
```

Prepare data for plot and plot temperature and effective temperature over time
```{r echo=TRUE, message=FALSE, warning=FALSE}
karachi_June2015_plot <- karachi_June2015 %>% 
  select(Date.Time, DBT, T.Air_None, T.Air_Passive) %>%
  filter(DBT != 25) %>%
  mutate(WHO = 30) %>%
  pivot_longer(!Date.Time, names_to = "Type", values_to = "Temperature") %>%
  mutate(Type = factor(Type, levels = c("DBT", "WHO", "T.Air_None", "T.Air_Passive")))

karachi_timeseries_plot <- ggplot(karachi_June2015_plot, aes(x = Date.Time, y = Temperature)) + 
  annotate("rect", xmin = parse_date_time("2015-06-17 0:00", "ymd_HM"), xmax = parse_date_time("2015-06-24 0:00", "ymd_HM"), ymin = -Inf, ymax = Inf, alpha = 0.2, fill = "#FDDBC7") +
  annotate("text", x = parse_date_time("2015-06-17 12:00", "ymd_HM"), y = Inf, label = "Heat Wave") +
  geom_line(aes(linetype = Type, colour = Type)) +
  scale_colour_manual(values = c("#D9F0D3", "#e7d4e8", "#000000", "#ee833d")) +
  scale_x_datetime(date_breaks = "2 day", date_labels = "%b %d", limits = c(parse_date_time("2015-06-14", "ymd"), parse_date_time("2015-06-27", "ymd"))) +
  scale_y_continuous(breaks = seq(25, 45, 5), limits = c(25, 45)) +
  theme_custom() +
  theme(axis.title = element_blank()) +
  theme(panel.grid.major.y = element_line(colour = "#f7f7f7"))
```

Combine plots to form Figure 2 in paper
```{r echo=TRUE, message=FALSE, warning=FALSE}
right <- ggarrange(karachi_exposure_plot, dallas_exposure_plot, legend = "none", nrow = 2, ncol = 1, align = "hv", labels = c("ii", "ii"))

left <- ggarrange(karachi_timeseries_plot, dallas_timeseries_plot, legend = "none", nrow = 2, ncol = 1, align = "hv", labels = c("i", "i"))

ggarrange(left, right, widths = c(3, 2), ncol = 2, nrow = 1)
```

