---
title: "DataAnalysis"
author: "Arfa Aijazi"
date: "2/24/2022"
output: html_document
---

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
```

Read HOBO data
```{r echo=TRUE, message=FALSE, warning=FALSE}
hobo_dir <- "data/Experiment/hobo"
merged_hobo <- list()

for (i in 1:4){
  files_hobo <- list.files(path = hobo_dir, pattern = paste0("*_", i, ".csv"), full.names = TRUE)
  
  if(i == 1){
    colNames_hobo <-c("Number", "Time", "Hobo_1.3", "Hobo_1.4", "HostConnected", "Stopped", "EndOfFile")
  }
  
  else{
    colNames_hobo <- c("Number", "Time", paste0("Hobo_",i), "HostConnected", "Stopped", "EndOfFile")
  }
  
  data_hobo <- lapply(files_hobo, read_csv, skip = 2, col_names = colNames_hobo, col_types = cols())
  merged_hobo[[i]] <-data_hobo %>%
    reduce(full_join) %>%
    select(-Number, -HostConnected, -Stopped, -EndOfFile) %>%
    pivot_longer(cols = starts_with("Hobo_"), names_to = "Hobo", values_to = "Temperature_F")
  
}

data_hobo <- merged_hobo %>%
  reduce(full_join) %>%
  mutate(Temperature_C = (Temperature_F-32)*5/9) %>%
  mutate(Time = mdy_hms(Time)) %>%
  mutate(Hobo = parse_number(Hobo)) %>%
  select(-Temperature_F)

rm(merged_hobo) 
```
Hobo calibration
```{r}
calibration_dir <- "calibration/hobo"
merged_calibration <- list()

for (i in 1:4){
  files_calibration <- list.files(path = calibration_dir, pattern = paste0("*_", i, ".csv"), full.names = TRUE)
  
  if(i == 1){
    colNames_hobo <-c("Number", "Time", "Hobo_1.3", "Hobo_1.4", "HostConnected", "Stopped", "EndOfFile")
  }
  
  else{
    colNames_hobo <- c("Number", "Time", paste0("Hobo_",i), "HostConnected", "Stopped", "EndOfFile")
  }
  
  data_calibration <- lapply(files_calibration, read_csv, skip = 2, col_names = colNames_hobo)
  merged_calibration[[i]] <-data_calibration %>%
  reduce(full_join) %>%
  select(-Number, -HostConnected, -Stopped, -EndOfFile) %>%
  pivot_longer(cols = starts_with("Hobo_"), names_to = "Hobo", values_to = "Temperature_F")
  
}

calibration_hobo <- merged_calibration %>%
  reduce(full_join) %>%
  mutate(Temperature_C = (Temperature_F-32)*5/9) %>%
  mutate(Hobo = parse_number(Hobo)) %>%
  mutate(Time = case_when(Hobo == 4 ~ mdy_hm(Time),
                          TRUE ~ mdy_hms(Time))) %>%
  select(-Temperature_F)

rm(merged_calibration)
rm(data_calibration)
```

```{r}

startStop <- read_csv("calibration/startstop.csv")

hobo_meanDiff <- calibration_hobo %>%
  left_join(startStop) %>%
  mutate(across(c(starts_with("Start_"), starts_with("End_")), mdy_hm)) %>%
  mutate(steady_15 = ifelse(Time > Start_15 & Time < End_15, TRUE, FALSE)) %>%
  mutate(steady_25 = ifelse(Time > Start_25 & Time < End_25, TRUE, FALSE)) %>%
  mutate(steady_35 = ifelse(Time > Start_35 & Time < End_35, TRUE, FALSE)) %>%
  mutate(steady = ifelse(steady_15 == TRUE | steady_25 == TRUE | steady_35 == TRUE, TRUE, FALSE)) %>%
  filter(steady == TRUE) %>%
  mutate(steadyT = case_when(steady_15 == TRUE ~ 15,
                            steady_25 == TRUE ~ 25, 
                            steady_35 == TRUE ~ 35)) %>%
  mutate(difference = Temperature_C - steadyT) %>%
  mutate(steadyT = factor(steadyT)) %>%
  group_by(Hobo, steadyT) %>%
  slice_sample(n = 200) %>%
  summarise(n = n(), meanT = mean(Temperature_C), meanDiff = mean(difference)) %>%
  group_by(Hobo) %>%
  summarise(meanDiff = mean(meanDiff))

```

```{r}
cal_data_hobo <- data_hobo %>%
  left_join(hobo_meanDiff) %>%
  mutate(cal_Temperature_C = Temperature_C + meanDiff)
```

```{r}
plot_hobo <- cal_data_hobo %>%
  mutate(Position = case_when(Hobo == 1.3 ~ "Head",
                                Hobo == 1.4 ~ "Back",
                                Hobo == 2 ~ "LowerLeg",
                                Hobo == 3 ~ "Chest",
                                Hobo == 4 ~ "Pelvis")) %>%
  filter(between(cal_Temperature_C, 15, 29))

ggplot(plot_hobo, aes(x = Time, y = cal_Temperature_C)) +
  geom_line(aes(colour = Position)) +
  geom_hline(yintercept = c(16, 24, 28)) +
  theme_minimal() +
  theme(legend.position = "top", panel.grid = element_blank()) +
  xlab("") +
  ylab("Temperature (degC)")
```

Read thermal manikin data
```{r echo=TRUE, message=FALSE, warning=FALSE}
manikin_dir <- "data/Experiment/manikin"

files_manikin <- list.files(path = manikin_dir, pattern = "*_Experiment.csv", full.names = TRUE)

colNames_manikin <- read_csv("ColumnNames.csv", col_names = F)

data_manikin <- lapply(files_manikin, read_csv, skip = 5, col_names = colNames_manikin$X1)
merged_manikin <- reduce(data_manikin, full_join)
  
  
data_manikin <- merged_manikin %>%
  select(-ends_with(".Clo"), 
         -ends_with(".Teq"), 
         -ends_with(".PMV"), 
         -ends_with(".PPD"), 
         -ends_with(".SET"), 
         -ends_with(".ET"), 
         -starts_with("All"), 
         -starts_with("GroupA"), 
         -starts_with("GroupB"),
         -Runtime) %>%
  mutate(Time = mdy_hms(Time)) %>%
  drop_na(Time) %>%
  pivot_longer(cols = ends_with(".T") | ends_with(".P"),
               names_to = c("BodySegment", "Metric"),
               names_sep = "[.]") %>%
  pivot_wider(names_from = Metric, names_prefix = "Metric.", values_from = value)

rm(merged_manikin) 
```

Read Experimental Matrix
```{r}
experimental_matrix <- read_csv("data/ExperimentalMatrix.csv") %>%
  mutate(Start.Time = mdy_hm(Start.Time)) %>%
  mutate(End.Time = mdy_hm(End.Time)) %>%
  mutate(Alias = paste(Chamber.SetPoint, Clothing, Bedding, Posture, Emergency.Blanket, Bed.Type, PCS, Repetition, sep = "_"))

glimpse(experimental_matrix)
```

Calculate h
```{r}
reference <- experimental_matrix %>%
  filter(Reference == TRUE) %>%
  drop_na(Start.Time) %>%
  select(Chamber.SetPoint, Posture, Repetition, End.Time) %>%
  mutate(T.ambient = 0) %>%
  mutate(h.Back = 0) %>%
  mutate(h.Chest = 0) %>%
  mutate(h.Head = 0) %>%
  mutate(h.LFoot = 0) %>%
  mutate(h.LForearm = 0) %>%
  mutate(h.LHand = 0) %>%
  mutate(h.LLowLeg = 0) %>%
  mutate(h.LThigh = 0) %>%
  mutate(h.LUpperArm = 0) %>%
  mutate(h.Pelvis = 0) %>%
  mutate(h.RFoot = 0) %>%
  mutate(h.RForearm = 0) %>%
  mutate(h.RHand = 0) %>%
  mutate(h.RLowLeg = 0) %>%
  mutate(h.RThigh = 0) %>%
  mutate(h.RUpperArm = 0)

# reference_hobo <- data.frame(Chamber.SetPoint = double(),
#                              Posture = character(),
#                              Repetition = double(),
#                              Hobo = double(),
#                              cal_Temperature_C = double())
# reference_manikin <- data.frame(Chamber.SetPoint = double(),
#                                 Posture = character(),
#                                 Repetition = double(),
#                                 BodySegment = character(),
#                                 Metric.T = double(),
#                                 Metric.P = double())

for (i in 1:nrow(reference)) {
  subset_hobo <- cal_data_hobo %>%
    filter(between(Time, reference$End.Time[i]-minutes(11), reference$End.Time[i]-minutes(1))) %>% # drop last 1 minute and average over the previous 10 minutes
    filter(between(cal_Temperature_C, reference$Chamber.SetPoint[i]-1, reference$Chamber.SetPoint[i]+1))
  # reference_hobo <- full_join(reference_hobo, 
  #                            data.frame(Chamber.SetPoint = reference$Chamber.SetPoint[i],
  #                                       Posture = reference$Posture[i],
  #                                       Repetition = reference$Repetition[i],
  #                                       Hobo = subset_hobo$Hobo,
  #                                       cal_Temperature_C = subset_hobo$cal_Temperature_C))
  #
  
  reference$T.ambient[i] <- mean(subset_hobo$cal_Temperature_C)
  
  subset_manikin <- data_manikin %>%
    filter(between(Time, reference$End.Time[i]-minutes(11), reference$End.Time[i]-minutes(1)))  %>%
    group_by(BodySegment) %>%
    summarise(Mean.T = mean(Metric.T), Mean.P = mean(Metric.P)) %>%
    mutate(h = Mean.P/(Mean.T - reference$T.ambient[i])) %>%
    select(-Mean.P, -Mean.T) %>%
    pivot_wider(names_from = BodySegment, names_prefix = "h.", values_from = h)
  reference[i,6:21] <- subset_manikin
  
  # reference_manikin <- full_join(reference_manikin, 
  #                            data.frame(Chamber.SetPoint = reference$Chamber.SetPoint[i],
  #                                       Posture = reference$Posture[i],
  #                                       Repetition = reference$Repetition[i],
  #                                       BodySegment = subset_manikin$BodySegment,
  #                                       Metric.T = subset_manikin$Metric.T,
  #                                       Metric.P = subset_manikin$Metric.P))
}


```

```{r}
plot_reference_hobo <- reference_hobo %>%
  mutate(Chamber.SetPoint = factor(Chamber.SetPoint)) %>%
  mutate(Repetition = factor(Repetition)) %>%
  mutate(Hobo = factor(Hobo))

ggplot(plot_reference_hobo, aes(x = Chamber.SetPoint, y = cal_Temperature_C)) +
  geom_boxplot() +
  geom_hline(yintercept = c(16, 28)) +
  theme_minimal() +
  theme(legend.position = "top")

```


Variability of T and P across four repetitions of reference condition at 16 C in log position
```{r}
variability_16_log <- reference %>%
  filter(Chamber.SetPoint == 16) %>%
  filter(Posture == "Log") %>%
  select(Repetition, starts_with("h.")) %>%
  pivot_longer(cols = starts_with("h."),
               names_to = "BodySegment",
               names_prefix = "h.",
               values_to = "h") %>%
  mutate(h = round(h, 2)) %>%
  pivot_wider(names_from = Repetition,
              names_prefix = "Repetition.",
              values_from = "h") %>%
  rowwise() %>%
  mutate(h.mean = mean(c(Repetition.1, Repetition.2, Repetition.3, Repetition.4))) %>%
  mutate(h.min = min(c(Repetition.1, Repetition.2, Repetition.3, Repetition.4))) %>%
  mutate(h.max = max(c(Repetition.1, Repetition.2, Repetition.3, Repetition.4))) %>%
  mutate(h.diff = h.max - h.min) %>%
  mutate(h.perVariability = h.diff/h.mean)

```

Variability of h across four repetitions of reference condition at 16 C in fetal position
```{r}
variability_16_fetal <- reference %>%
  filter(Chamber.SetPoint == 16) %>%
  filter(Posture == "Fetal") %>%
  select(Repetition, starts_with("h.")) %>%
  pivot_longer(cols = starts_with("h."),
               names_to = "BodySegment",
               names_prefix = "h.",
               values_to = "h") %>%
  mutate(h = round(h, 2)) %>%
  pivot_wider(names_from = Repetition,
              names_prefix = "Repetition.",
              values_from = "h") %>%
  rowwise() %>%
  mutate(h.mean = mean(c(Repetition.1, Repetition.2, Repetition.3, Repetition.4))) %>%
  mutate(h.min = min(c(Repetition.1, Repetition.2, Repetition.3, Repetition.4))) %>%
  mutate(h.max = max(c(Repetition.1, Repetition.2, Repetition.3, Repetition.4))) %>%
  mutate(h.diff = h.max - h.min) %>%
  mutate(h.perVariability = h.diff/h.mean)


```

Variability of h across four repetitions of reference condition at 28 C in log position
```{r}
variability_28_log <- reference %>%
  filter(Chamber.SetPoint == 28) %>%
  filter(Posture == "Log") %>%
  select(Repetition, starts_with("h.")) %>%
  pivot_longer(cols = starts_with("h."),
               names_to = "BodySegment",
               names_prefix = "h.",
               values_to = "h") %>%
  mutate(h = round(h, 2)) %>%
  pivot_wider(names_from = Repetition,
              names_prefix = "Repetition.",
              values_from = "h") %>%
  rowwise() %>%
  mutate(h.mean = mean(c(Repetition.2, Repetition.3, Repetition.4))) %>%
  mutate(h.min = min(c(Repetition.2, Repetition.3, Repetition.4))) %>%
  mutate(h.max = max(c(Repetition.2, Repetition.3, Repetition.4))) %>%
  mutate(h.diff = h.max - h.min) %>%
  mutate(h.perVariability = h.diff/h.mean)

```

Variability of h across four repetitions of reference condition at 28 C in starfish position
```{r}
variability_28_starfish <- reference %>%
  filter(Chamber.SetPoint == 28) %>%
  filter(Posture == "Starfish") %>%
  select(Repetition, starts_with("h.")) %>%
  pivot_longer(cols = starts_with("h."),
               names_to = "BodySegment",
               names_prefix = "h.",
               values_to = "h") %>%
  mutate(h = round(h, 2)) %>%
  pivot_wider(names_from = Repetition,
              names_prefix = "Repetition.",
              values_from = "h") 

```

Plot h by posture and chamber set point temperature
```{r}
reference_plot <- reference %>%
  filter(is.nan(T.ambient) == FALSE) %>%
  filter(T.ambient != 0) %>%
  select(Chamber.SetPoint, Posture, Repetition, T.ambient, starts_with("h.")) %>%
  group_by(Chamber.SetPoint, Posture) %>%
  summarise(n = n(), across(c(T.ambient, starts_with("h.")), mean)) %>%
  pivot_longer(cols = starts_with("h."), names_to = "BodySegment", names_prefix = "h.", values_to = "h")

ggplot(reference_plot, aes(x = BodySegment, y = h)) +
  geom_col(aes(fill = Posture), position = position_dodge2(width =0.5)) +
  facet_grid(.~Chamber.SetPoint) +
  coord_flip() +
  theme_minimal() +
  theme(legend.position = "top") +
  xlab("") +
  ylab(expression(h~(W/m^2~degree*C)))

```
Calculate Teq
```{r}
h_reference <- reference %>%
  filter(is.nan(T.ambient) == FALSE) %>%
  filter(T.ambient != 0) %>%
  group_by(Chamber.SetPoint, Posture) %>%
  summarise(across(c(starts_with("h.")), mean))
```

```{r}
teq_cal <- experimental_matrix %>%
  filter(Reference == FALSE) %>%
  left_join(h_reference) %>%
  select(-Random.Number, -Reference, Notes, Comments, IR.Image) %>%
  drop_na(Start.Time) %>%
  mutate(T.ambient = 0) %>%
  mutate(T.eq = 0)

SurfaceArea <- read_csv("SurfaceArea.csv")

for (i in 1:nrow(teq_cal)) {
  subset_hobo <- cal_data_hobo %>%
    filter(between(Time, teq_cal$End.Time[i]-minutes(11), teq_cal$End.Time[i]-minutes(1))) %>% # drop last 1 minute and average over the previous 10 minutes
    filter(between(cal_Temperature_C, teq_cal$Chamber.SetPoint[i]-1, teq_cal$Chamber.SetPoint[i]+1))
  
  teq_cal$T.ambient[i] <- mean(subset_hobo$cal_Temperature_C)
  
  subset_h <- teq_cal[i,] %>%
    select(starts_with("h")) %>%
    pivot_longer(cols = starts_with("h."), names_to = "BodySegment", names_prefix = "h.", values_to = "h")
  
  
  subset_manikin <- data_manikin %>%
    filter(between(Time, teq_cal$End.Time[i]-minutes(11), teq_cal$End.Time[i]-minutes(1))) %>%
    group_by(BodySegment) %>%
    summarise(Mean.T = mean(Metric.T), Mean.P = mean(Metric.P)) %>%
    left_join(subset_h) %>%
    mutate(T.eq = Mean.T - (Mean.P/h)) %>%
    left_join(SurfaceArea)
  
  teq_cal$T.eq[i] =  sum(subset_manikin$T.eq*subset_manikin$SurfaceArea)/sum(subset_manikin$SurfaceArea)
}
  
```
```{r}
baseline <- teq_cal %>%
  filter(Baseline == TRUE) %>%
  group_by(Chamber.SetPoint) %>%
  summarise(baseline.mean = mean(T.eq), baseline.margin = qt(0.975,df=n()-1)*sd(T.eq)/sqrt(n())) %>%
  mutate(baseline.upper = baseline.mean + baseline.margin) %>%
  mutate(baseline.lower = baseline.mean - baseline.margin)
  
```

```{r}
thermal_effect <- teq_cal %>%
  left_join(baseline) %>%
  filter(Baseline == FALSE) %>%
  select(1:9, Alias, T.ambient, T.eq, starts_with("baseline.")) %>%
  mutate(effect.mean = T.eq - baseline.mean) %>%
  mutate(effect.lower = T.eq - baseline.lower) %>%
  mutate(effect.upper = T.eq - baseline.upper) %>%
  arrange(effect.mean) %>%
  mutate(Alias = factor(Alias, levels = Alias)) %>%
  mutate(Chamber.SetPoint = factor(Chamber.SetPoint))

```
```{r}
ggplot(thermal_effect, aes(x = Alias, y = effect.mean)) +
  geom_point(aes(colour = Chamber.SetPoint)) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  theme_minimal() +
  theme(panel.grid = element_blank(), legend.position = "none") +
  ylab("Whole-body thermal effect (degC)")
```

